
\section{Video Editing Computer}
Video editing doesn't require an expensive computer, especially if you're a beginner. You'll need a decent monitor and video card, which come installed on most new computers. If you have an older computer, check it against your video editing software specifications to make sure it will work for video editing.
Unfortunately, many older computers simply aren't fast enough for it, and you'll need to upgrade your whole system.

\section{Storage Space on the Video Editing Computer}
Digital video footage - especially high-definition footage - takes up a lot of drive space, and you'll need somewhere to put it.
An external hard drive is one way to solve that problem. But if you buy a video editing computer with a lot of internal drive space, you can put off buying the external hard drive for a while.
Your Plans for the Video Editing Computer
Before you buy a video editing computer, consider the projects that you plan to create.
If you only plan on editing basic videos using free software like Movie Maker or iMovie, most new computers out there have the right inputs and plenty of storage space to fit your needs.
If you plan on editing with more powerful professional editing software, you’ll want a computer that gives you more processing power.

Free video editing software is an easy and convenient way to edit your videos, and is great for beginners. Most of the free video editing programs have limited editing features, so after a while you may want to look at the mid-level digital video softwareor the top professional video editing programs.
iMovie
iMovie comes free with new Macs. iMovie offers many options for editing video and audio, and adding photos, music and narration to your movies. 
Movie Maker
Movie Maker is Window's free video editing software, which comes installed on new PCs. Use the program to create and share high-quality movies. 
YouTube
YouTube's video editor is an easy, free way to trim clips or remix videos. The editing power is limited, though, and you'll never get an uncompressed version of the final product. 
Pinnacle SpinVideo Spin, for PCs, is free video editing software from Pinnacle. Video Spin is specifically designed to take the complexity out of video editing, but it still includes tools, transitions and effects so you can easily jazz up your videos.
Free Online Editing SoftwareBesides YouTube, there are several other web applications that provide free video editing online. These services are great for re-editing and re-mixing web videos, and some even offer to produce DVDs of your edited videos.



